SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-08 docs/questioning.tex
discussing the overhead

  &   {\it NoForge}~\cite{JKK06a} & 35 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} & {\sc csrf} \\

@@

  &   {\it CsFire}~\cite{DDHPJ10} & 35 & (419582,1141807,0,3)\_r\tnote{4} & {\sc na} & {\sc csrf} \\

@@

  &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc sql} injection \\

@@

There are also authors that took a different approach.
For instance, during their initial tests,
Stock et al.~\cite{SLMS14} managed to bypass
the browser-based {\sc xss} filters of the
73\% of 1,602 real-world {\sc dom}-based {\sc xss} vulnerabilities.
These vulnerabilities were actually found during
their previous research~\cite{LSJ13}.
Finally, in the publications that
{\sc amnesia}~\cite{HO05,HO06,HO05b}
and {\sc sd}river~\cite{MS09,MKS09,MKLS11} were presented,
authors managed to break existing application suites
and then test the diagnostic performance of their tools on them.

@@

>>>>

  &   {\it NoForge}~\cite{JKK06a} & 35 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} ({\sc s}) & {\sc csrf} \\

@@

  &   {\it CsFire}~\cite{DDHPJ10} & 35 & (419582,1141807,0,3)\_r\tnote{4} & {\sc na} ({\sc c}) & {\sc csrf} \\

@@

  &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql} injection \\

@@

There are also authors that took a different approach.
For instance, during their initial tests,
Stock et al.~\cite{SLMS14} managed to bypass
the browser-based {\sc xss} filters of the
73\% of 1,602 real-world {\sc dom}-based {\sc xss} vulnerabilities.
These vulnerabilities were actually found during
their previous research~\cite{LSJ13}.
Finally, in the publications that
{\sc amnesia} and {\sc sd}river were presented,
authors managed to break existing application suites
and then test the diagnostic performance of their tools on them.

@@

Table~\ref{tab:comp} shows for every mechanism its
corresponding overhead. In addition, it indicates
if the overhead is applied to the server-side ({\sc s}),
or the client-side ({\sc c}).
Our first observation, is that there is a differential
in the way in which the computational overhead of the
mechanisms is measured. In many cases, 16 out of
34 (47.05\%), the overhead is provided as a percentage
while in other cases, 7 our of 34 (20.5\%),
the authors provide the time (in terms of ms) that
their mechanisms add to the normal execution time of
the protecting entity. Surprisingly, in 10 cases (29,4\%),
the overhead was either not available ({\sc na}) or
not quantified ({\sc nq}). In the case of {\sc php aspis},
its authors indicate that with their mechanism,
the execution time is doubled.
